Aspects of RDF Data Constraints in the Social, Behavioural and Economic Sciences

### 2015-04-29 paper/paper7/paper7.tex
evaluation

>>>>

In this paper, we discuss constraints on RDF data in general. Note that the data represented in RDF can be data in the sense of SBE sciences, but also metadata about published or unpublished data. We generally refer to both simply as RDF data and only distinguish between data and metadata in the dataset descriptions and in the case that it matters for the purpose of this paper.\tb{hab ich eingefügt, ist der absatz von dir...}
